### 2020-06-28 design.tex
intro and design

As mentioned above, we designed merging layers in our network so that we can process the input images by performing convolution operations to each single image, and then merging them together. The merged data will be stacked with the feature maps of each single image before we perform the next layer of convolution on them. Each convolutional layer uses the same set of parameters for all the images, so that the same set of features are extracted from the images, and thus can be merged. The merging layers consists of simple calculations extracting either the most significant, or the mutual features of the images, the former preserving interesting findings while the latter filters out credible features from the redundancy of the input. The network pipeline consists of alternate layers of convolution and merging, and after each merging layer, the reliable information accumulates and more complex features can be extracted with their support. Furthermore, we frequently insert the original input images in each level of our pipeline, creating an unevenness in depth and reducing network complexity, because we discovered that this process guides the model to be loyal to the inputs, generating more truthful results and less artifacts.

The details of our network architecture is as follows:
	Each input image (or each lane from the output of the previous layer) is assigned to its own lane and processed by several convolutional layers. These layers share parameters across channels; however, each image is processed individually and do not interact with each other in this stage. Each channel will present a feature map of n channels.
	The features extracted from all layers are merged broadwise with the following function:

    $${x'_k=\sum x_ie^{kx_i}/\sum e^{kx_i}}$$

Where k varies from -1 to 1. Apparently, k=0 leads to averaging, k=${+\infty}$ leads to a process similar to max operator and k=${-\infty}$ leads to min operator. This process merges information from every lane into one. The output is n channels for each value of k. 
	The original input images are accessed again. These images are also processed separately by several convolutional layers (sharing parameters across lanes) to extract features. The output of these images (m channels each) are stacked with the n channels from step 2) as m+n channels each lane. Some more convolution and an upscaling layer may follow, merging the data more thoroughly. These will be the input for the next layer.
The above 3 steps are stacked as one layer. The functional network often consists of 5 to 8 layers to achieve 4x super resolution. The network ends with a merging process similar to the 2) step and a few more layers of convolution. The full structure of a 3 layer network is shown in Fig~\ref{fig-system}.

>>>>

The core of the \textsf{SRPeek} system is a specially designed multi-frame SR neural network, accepting a group of $N$ images indexed $x_1^{(0)}$ to $x_N^{(0)}$ as input and generating an image with higher resolution $y$ as output. The network comprises $L$ layers, each of which implements a non-linear transformation $H_l(\cdot)$, where $l$ indexes the layer. As mentioned before, in each layer images are processed separately, with the merging layers as a revenue for communication, so that the output of each layer is correspondent to the input.  We denote the output of the $l^{th}$ layer as $x_1^{(l)}$ to $x_N^{(l)}$, which is also the input of the $(l+1)^{th}$ layer. Till now the model is not different from traditional SR models:

$$x_i^{(l)} = H_l(x_i^{(l-1)}), i=1,2,...N$$

\cl{function above cannot express merging between x1 x2 ... xN?}

Additionally, we introduce the initial images $x_i^{(0)}$ as an input for all the layers:

$$x_i^{(l)} = H_l(x_i^{(l-1)},x_i^{(0)}), i=1,2,...N$$

The last layer is exceptional, it yields a single image $y$ as output.

Presently, in these layers nothing is done to raise the resolution of the images, so that the resolution of $x_i^{(0)}$ to $x_i^{(l-1)}$ and $y$ remains the same. To increase resolution we insert several 2$\times$ nearest upsampling layers $U$ evenly throughout the architecture between the layers:

$$x_i^{(l)} \leftarrow U(x_i^{(l)}), x_i^{(0)} \leftarrow U(x_i^{(0)}), i=1,2,...N$$

we upsample the input images $x_i^{(0)}$ simultaneously to keep the two inputs of the following layers $H_l(x_i^{(l-1)},x_i^{(0)})$ unanimous in resolution. For example, in a 4$\times$ SR network with five layers, we may insert 2 2$\times$ nearest upsampling layers behind the 2nd and 4th layer.

Inside each layer $H_l$ there are 3 convolution layers $Conv_{1l}(\cdot)$, $Conv_{2l}(\cdot)$, $Conv_{3l}(\cdot)$ and 1 merging layer $Merge_l(\cdot)$, distributed as follows:

\cl{$H(\cdot)$ or $H(\cdot,\cdot)$?}

\begin{enumerate}
\item The first input parameter of this layer, $x_i^{(l-1)}$, is passed through a convolution layer to extract features. Note that all three convolutional layers accept a single image(or its featuremaps from the last convolutional layer) as input, the convolutional process is repeated for all the images, and calculations within the same convolutional layer share the same group of parameters all the time (parameters denoted as $Param_{sl}$ for convolutional layer $Conv_{sl}, s=1,2,3$):

$$ a_i^{(l)} = Conv_{1l}(x_i^{(l-1)},Param_{1l}), i=1,2,...N$$

\item The results of the previous step of all the images $\{a_1^{(l)},a_2^{(l)},...,a_n^{(l)}\}$ are then passed to the merging layer $Merge_l$ to generate $t$ groups of featuremaps. Suppose the results of $Conv_{1l}$ consists of $R$ channels:

$$ a_i^{(l)} = \{a_{i1}^{(l)},a_{i2}^{(l)},...,a_{iR}^{(l)}\}, i=1,2,...N$$

The data in each channel will be merged separately in the merging layer. The output is $T\times R$ channels, denoted as $b_{tr}^{(l)}(t=1,2,...T, r=1,2,...R)$:

$$ b_{tr(p,q)}^{(l)} = \sum_{i=1}^{N} a_{ir(p,q)}^{(l)} e^{k_t a_{ir(p,q)}^{(l)}} /\sum e^{k_t a_{ir(p,q)}^{(l)}},$$
$$ p=1,2,...P, q=1,2,...Q, t=1,2,...T, r=1,2,...R $$

$P,Q$ denotes the height and width of the current images, (p,q) represent the pixel located at this coordinate, and $k_t$ is a set of fixed parameters shared in all the merging layers throughout the model, controlling the behavior of the merging process. Apparently, k=0 leads to averaging, k=${+\infty}$ leads to max operator and k=${-\infty}$ leads to min operator. We use T=5 and k=-1,-0.5,0,0.5,1 in our model, giving consideration to both consensuses (k=0,averaging) and prominent features(k=1, 'soft'max and k=-1, 'soft'min). these $T\times R$ channels $b_{tr}^{(l)}$ is the output of this merging layer $Merge_l$.

\item Separately, we pass the initial input images, $$x_i^{(0)}$$, or the second input parameter of $H_l$ into a convolutional layer$Conv_{2l}$, which is similar to $Conv_{1l}$ and process each image separately, also generating $N$ outputs with $R$ channels per output, denoted as $$c_ir^{(l)}, i=1,2,...N, r=1,2,...R$$:

$$ c_i^{(l)} = Conv_{2l}(x_i^{(0)},Param_{2l}), i=1,2,...N$$

$$ c_i^{(l)} = \{c_{i1}^{(l)},c_{i2}^{(l)},...,c_{iR}^{(l)}\}, i=1,2,...N$$

\item The data from step (2) and (3) are merged together, in that all the $T\times R$ channels of $b_{tr}^{(l)}$ are replicated N times and stacked with each one of the N outputs of $Conv_{2l}$, before these N outputs, each with $(T+1)\times R$ channels, are passed through the third convolutional layer $Conv_{3l}$. There are also N output of this convolutional layer, denoted as $d_i^{(l)}, i=1,2,...N$:

$$ d_i^{(l)} = Conv_{3l}(Stack(c_i^{(l)},b^{(l)}),Param_{3l}), i=1,2,...N $$

\item If $l < L$, this is not the last layer, the N outputs of step (4) will be the output of layer $H_l$. Otherwise, as we need to present a single image $y$ as output, we add another merging and a common convolutional layer after $Conv_{3l}$. The merging layer is identical to the previous $Merge_l$, merging the N outputs $d_i^{(l)}$ into $T\times R$ channels $e_{tr}^{(l)}$, and a convolutional layer processes this $e_{tr}^{(l)}$ to generate a single channel of output $y$.

$$ \{e_{tr}^{(L)},t\in (1,T),r\in (1,R)\} = Merge`_{L}(\{d_i^{(L)},i\in (1,N)\})$$

$$ y = Conv`_{L}(\{e_{tr}^{(L)},t\in (1,T),r\in (1,R)\})$$

The full structure of a 3 layer network is shown in Fig~\ref{fig-system}.

### 2020-06-28 introduction.tex
intro and design

% introduce LPL asynchronous duty cycle media access
As already we are aware, smartphones have become a necessity in our lives, as we are checking our mobile phones constantly throughout the day. As a result, some privacy concerns have arisen about nearby parties peeking at our screen, namely ``shoulder surfing". 
Assuming that the attacker is not malicious and merely takes several peeks out of curiosity, most works in this area are built on a threat model of an attacker observing with naked eyes. And studies show that a great portion of these attacks are casual and opportunistic without technical equipment~\cite{eiband2017understanding}, say a mere stranger can hardly do any harm reading a fragment of the correspondence or acquiring the password without knowing the account for critical apps like Alipay, which seldom appears on screen in common usages. 
% It is however the rare but malicious attacker, with certain familiarity and knowledge of the victim, that can do the most harm. The attacker can even be our closest friends or family members, as there are various cases in China where a child obtains Alipay password of their parents and is unaware that electronic payments consists of 'real' money, resulting in spending them lavishly in their games. Besides, specially designed equipment are not a necessity for the shoulder surfing attack.

@@

\cl{The challenge part can be revised to make it more precise. And it can be described with the new figure.}
\vspace{1mm}
\noindent
\textbf{challenges.} Creating a high-resolution shoulder surfing attack model running on commercial smartphones in real time, however, is not trivial. And we achieve \textsf{SRPeek} by overcoming three key challenges.

\begin{itemize}[leftmargin=*]
  \item \textbf{Blurriness of input images.} The most prominent one is the blurriness, as our photos are taken at extreme range, taken secretly and hurriedly without much room for focusing, while straining the magnification of the smartphone lenses. Unlike most SR applications and datasets working with ‘normally’ captured photos, the images we face exhibit lower concentrations of information and more artifacts, and needs more ‘reconstruction’ than ‘interpolation’.
  \item \textbf{Processing with multi-frames.} While exploring this privacy threat, we need a multi-frame SR algorithm on a smartphone to monitor the target phone in real time. However, we discover that there is no existing SR algorithm suitable for this scenario. On one hand, images captured by hand are blurred while most methods rely on a handful of clearer images (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}. Specifically, we have to extract the information from large quantities of extremely blurred photos, as smartphones can capture 100 snapshots in a few seconds in burst mode, and these photos are taken from extreme distances. On the other hand, the difference between videos and multiple snapshots rules out the video super resolution algorithms, which cannot be adapted to larger numbers of input images. The reason has two folds. First, either increased input leads to increases in model complexity, making it unsuitable for mobile deployment. Second, they lack an emphasis on the process of horizontal comparison(??) by relying heavily on the information extracted from each single image, resulting in an inefficient merge of information from multiple frames.
  \item \textbf{Compatibility with various characters.} Another difficulty unique to our task is the subject—mainly, Chinese characters. Composed of multiple strokes, these characters are distributed discretely in image space, not known to other entities, e.g. faces and natural objects. In some cases, messing up a stroke will not impact its readability, and in other cases shortening or lengthening a stroke even slightly will lead to a different character, leading to misunderstandings. And unlike most SR applications working on similarity (between their output and the ‘ground truth’), our goal is readability, and the network architecture and training process must be engineered accordingly.
\end{itemize}

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{pic/zeros.png}
    \caption{Photos of number ‘0’ on a screen at a distance of 1.5m, taken in quick succession from a still smartphone camera. All exhibit different blurriness and no consistency between neighboring frames.\cl{Figure should be replaced.}}
	\label{fig-zeros}
\end{figure}

\cl{The following part can correspond to challenges above. Remember to be precise and illustrative.}
In this paper, we present \textsf{SRPeek}, an end-to-end system of shoulder surfing for commercial smartphones. To fully explore this privacy threat with the multi-frame super resolution, we first design a deep learning architecture using convolutional neural network (CNN). With the specially designed network as core, we deliver a holistic system for shoulder surfing on a smartphone. Then it processes them with our neural network to generate a high-resolution image and repeats the process for constant monitoring. As the information of interest is mostly in the form of text (e.g., passwords or e-mails), our network is trained and evaluated on the task of reconstructing text, specifically, Chinese characters, English letters, and numbers, but we believe that this network architecture can function in all scenarios. Our system can also be used as a preprocessor for text-recognition applications when multiple images are available, such as real-time translation apps on a smartphone or text-recognition on self-driving cars.

To deal with massive frames of blurred images with limited computational resources on smartphones, we design an unique merging layer and place it between convolutional layers in the SR pipeline. Thus information can be extracted first from input images independently and then merged together, serving as a reference for the following convolutions.

As mentioned above, reconstructing images with high degrees of blurriness requires a unique approach. Most works on multi-frame SR function on video clips \cite{lucas2019generative} or multiple snapshots \cite{wronski2019handheld}, however, our application is subtly different from the two. Our dilemma is as follows: on one hand, each one of the photos we are to process is blurred with a randomly different PSF kernel, which, because of the extreme blurriness, cannot be approximated as a constant, isotropic gaussian kernel, and thus lacking consistency between neighboring frames, meaning that they cannot be processed as a video clip(see Figure~\ref{fig-zeros} ); on the other hand, because of the low concentration of information, the blurred photos are similar to pieces of a jigsaw puzzle, each containing only fractions of information, and the only chance of recovering the ground truth is by comparing each photo against others. If processed by common procedures enhancing the resolution of a series of snapshots—processing each one separately and merging them afterwards, few useful information can be extracted from each one of the images, and merging them will not produce satisfactory results.

Considering the unique challenges of our application, we believe that if these images are processed iteratively, alternating between the following two processes, our network will be able to solve this ‘jigsaw puzzle’:

\begin{enumerate}
  \item Every single image of the input collection will be processed solely (by several layers of CNN), with access of the output of step (2) of the last iteration;
  \item The processed results will be merged (with weighted averaging methods) and distributed to each photo for the next iteration.
\end{enumerate}

This architecture is beneficial to our task. On one hand, the deep learning part is assigned to each single image, reducing computational complexity and parameter growth, while receiving a global view of all the images, renewed at each layer, thanks to the merging process; on the other hand, information can be shared horizontally with weighted averaging methods, meaning no consideration of sequential order and no reliance of consistency between neighboring frames. Thus, this architecture solves the dilemma mentioned above, and proves perfectly functional in our application.

>>>>

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{pic/intro.png}
    \caption{Overview of the proposed shoulder surfing threat model.}
	\label{fig-zeros}
\end{figure}
% introduce LPL asynchronous duty cycle media access
As already we are aware, smartphones have become a necessity in our lives, as we are checking our mobile phones constantly throughout the day. As a result, some privacy concerns have arisen about nearby parties peeking at our screen, namely ``shoulder surfing". 
Assuming that the attacker is not malicious and merely takes several peeks out of curiosity, most works in this area are built on a threat model of an attacker observing with naked eyes. And studies show that a great portion of these attacks are casual and opportunistic without technical equipment~\cite{eiband2017understanding}, say a mere stranger can hardly do any harm reading a fragment of the correspondence or acquiring the password without knowing the account for critical apps like Alipay, which seldom appears on screen in common usages. 
% It is however the rare but malicious attacker, with certain familiarity and knowledge of the victim, that can do the most harm. The attacker can even be our closest friends or family members, as there are various cases in China where a child obtains Alipay password of their parents and is unaware that electronic payments consists of 'real' money, resulting in spending them lavishly in their games. Besides, specially designed equipment are not a necessity for the shoulder surfing attack.

@@

\cl{The challenge part can be revised to make it more precise. And it can be described with the new figure.}
\vspace{1mm}
\noindent
\textbf{challenges.} Creating a high-resolution shoulder surfing attack model running on commercial smartphones in real time, however, is not trivial. And we achieve \textsf{SRPeek} by overcoming three key challenges.
\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{pic/zeros.png}
    \caption{Photos of number ‘0’ on a screen at a distance of 1.5m, taken in quick succession from a still smartphone camera. All exhibit different blurriness and no consistency between neighboring frames.\cl{Figure should be replaced.}}
	\label{fig-zeros}
\end{figure}
\begin{itemize}[leftmargin=*]
  \item \textbf{Blurriness of input images.} \cl{need revising.} The most prominent one is the blurriness, as our photos are taken at extreme range, taken secretly and hurriedly without much room for focusing, while straining the magnification of the smartphone lenses. Unlike most SR applications and datasets working with ‘normally’ captured photos, the images we face exhibit lower concentrations of information and more artifacts, and needs more ‘reconstruction’ than ‘interpolation’. \cl{However, such blurry input means less information, and a greater possibility of reconstructing the wrong character. In deep learning based methods, a deep network often leads to gradual divergence from the truth as the data is propagated deeper through the network pipeline, resulting in 'fake' high-res images, especially when the subjects are the discrete strokes of characters, instead of details and texture of everyday objects. As a matter of fact, most works on multi-frame SR function on video clips \cite{lucas2019generative} or multiple snapshots \cite{wronski2019handheld}, however, our application is subtly different from the two. Our dilemma is as follows: on one hand, each one of the photos we are to process is blurred with a randomly different PSF kernel, which, because of the extreme blurriness, cannot be approximated as a constant, isotropic gaussian kernel, and thus lacking consistency between neighboring frames, meaning that they cannot be processed as a video clip(see Fig.~\ref{fig-zeros} ); on the other hand, because of the low concentration of information, the blurred photos are similar to pieces of a jigsaw puzzle, each containing only fractions of information, and the only chance of recovering the ground truth is by comparing each photo against others. If processed by common procedures enhancing the resolution of a series of snapshots—processing each one separately and merging them afterwards, few useful information can be extracted from each one of the images, and merging them will not produce satisfactory results.}	
  \item \textbf{Processing with multiple frames.} While exploring this privacy threat, we need a multi-frame SR algorithm on a smartphone to monitor the target phone in real time. However, we discover that there is no existing SR algorithm suitable for this scenario. On one hand, images captured by hand are blurred while most methods rely on a handful of clearer images (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}. Specifically, we have to extract the information from large quantities of extremely blurred photos, as smartphones can capture 10 snapshots per second in burst mode, and these photos are taken from extreme distances. On the other hand, the difference between videos and multiple snapshots rules out the video super resolution algorithms, which cannot be adapted to larger numbers of input images. The reason has two folds. First, either increased input leads to increases in model complexity, making it unsuitable for mobile deployment. \cl{Second, most models rely heavily on the information extracted from each single image, however, the images in our application are so blurry and distorted that we cannot tell if, for example, it is one stroke or two parrallel strokes that is shown in these two darker pixels on this photo---unless we consult pixels at the same location in other input photos. The nature of our task requires this kind of consultation of pixels with same coordinates on different images throughout our construction process, and this mechanism needs to be designed into the network architecture.}
  \item \textbf{Model complexity and variable input.} \cl{To achieve real-time monitoring, we need to perform our calculations locally on the smartphone, instead of sending the data to a server and process them remotely, because 1) the latter would require stable Internet access, and 2) sending multiple images across the Internet will consume time and bandwith. However, to get ideal results we need 10 to 20 images which will consume 1 to 2 seconds to capture, and this time period is the minimum interval between each output frame, with the processing phase working in parrallel. This way the time allowed for calculation is 1 to 2 seconds, with limited calculation power and RAM. In cases where the display on the target screen changes more frequently, less images will be avaliable for each scene, and the attacker requires more frequent feedback which means less time for each processing task. These not only require a smaller and simpler network model, but also a model that can function with variable input, efficiently utilizing the data from either 3 or 20 images and provide results to the best of its efforts.} 
  \item \textbf{Complexities of characters.} As the information of interest in shoulder surfing scenarios is mostly in the form of text (e.g., passwords or e-mails), we will focus on reconstructing text, specifically, Chinese characters, English letters, and numbers, in our system.\cl{declare this beforehand?} The task of reconstructing text, instead of scenary or objects, poses unique challenges. Composed of multiple strokes, these characters are distributed discretely in image space, not known to other entities, e.g. faces and natural objects. In some cases, messing up a stroke will not impact its readability, and in other cases shortening or lengthening a stroke even slightly will lead to a different character, leading to misunderstandings. And unlike most SR applications working on similarity (between their output and the ‘ground truth’), our goal is readability, and the network architecture and training process must be engineered accordingly.\cl{ Another challenge is imbalanced data. Among Chinese characters certain strokes and stroke groups are always more commonplace than others, and this imbalanceness often results in lower prediction accuracy over the less common,  unconventionality shaped characters. On the other hand, however, the focus on characters can also aid us. As our network is only expected to reconstructe these characters, the network can learn to detect features from the input and reconstruct strokes and segments from them, extracting more information from the blurry images.}
\end{itemize}

\cl{The following part can correspond to challenges above. Remember to be precise and illustrative.}
In this paper, we present \textsf{SRPeek}, an end-to-end system of shoulder surfing for commercial smartphones. Deployed on a smartphone, this system will take snapshots of the target screen in burst mode of the attacker's screen, which are aligned, cropped, and then processed by our multi-frame SR neural network to generate a high-res image of the victim's screen. The core of this system, the nerual network, is specifically designed and trained for this task, aimed to counter the four challenges mentioned above. The outline of this network is as follows:
\begin{itemize}[leftmargin=*]
  \item \textbf{Layered architecture and frequent introduction of input.} To counter the blurriness of the images, and the tendency of reconstructing fake characters, our network is constructed with several identical SR layers, connected sequentially, and the images are refined step by step throughout the layers. The input and output of each layer is also correspondent to each avaliable image\cl{???}, as all input images are processed simultaneously and separately(with the information from other images for reference) throughout the network, all the way to the end of the model where we merge all the data into one output image. Another importent feature of our architecture is that the initial input images are introduced into the dataflow at each layer, from beginning to end, resulting in the uneven depth of our model, acting as an anchor for the reconstruction process so that the output will be faithful to truth from beginning to end, while preserving the deep mainstream of the model to be able to process such blurry images.
  \item \textbf{Merging layers to adapt multiple frames.} The SR layer consists of several convolutional layers and a specially designed merging layer, which is the sole revenue of communication across images. As mentioned above, these images are processed individually thouroughout the network, and they are inputted from the last layer independently, convolutioned independently, and passed to the next layer independently. This apparently cannot fully utilize the information across the multiple frames, so that we design a merging process inside each SR layer, which merges featuremaps from all the images into one, and this data is distributed to each image in this layer and stacked with their featuremaps for the next convolution. In this way, during the refinement process of each of the images in every SR layer, the model has access to data of consensuses among other contemporary images, which can inspire the network to extract more prominent and collective features, and induce the convergence of all input images for increased seamlessness at the successing merging layer. In most deep learning architectures, the features extracted in each layer is more complex than the previous ones, the former's discoveries built on what the latter has achieved, and our model is not an exception; However, the merging layers we designed can support this increase. At each layer the image is exposed to the consensuses of features from other images at the same level of complexity, acting as a verification for the hypothetical features extracted from the current image, so that in the training process more audacious features can be learned and proposed without fear of punishment from the final loss, increasing the quality of featuremaps throughout the network.
  \item \textbf{Model Complexity and adaption for variable input.} All the convolutional layers throughout the network are thus designed: They are performed individually for each image(or the featuremaps of them from the previous layer), and these convolutions in the same layer share a same set of parameters in training and production, thus reducing parameter count and avoiding convolutions for large numbers of channels, saving calculation power. This also leads to the benefit that the output featuremaps of all the images are the evaluations over the same set of features\cl{???}, so that the merging process can also be accomplished easily without the need of trainable parameters. In our design, the merging layers consists of simple pixelwize processes resembling average, min and max processors, to filter out either the collective or the most prominent features among the featuremaps. This process functions with any number of input images. As the convolutional processes are also performed individually for each layer, the same set of parameters of the network model can function normally with any number of input images, while the calculation complexity also increases linearly with the amount of input. On one hand, this gives our model the ability to adapt to the uncertainty of the number of avaliable images, providing relatively satisfactory results regardless whether the attacker has ample time photographing the target phone before it changes its display; on the other hand, the relative independence and the isotropy of the merging layers avoids the reliance on sequential order and consistency between neighboring frames(which is common among most multi-frame SR networks), solving the inconsistency problem mentioned in Fig.~\ref{fig-zeros}.
  \item \textbf{Compatibility with complex characters.} The discrete distribution of characters leads to the inclination of diviation and producing 'fake' results. The frequent introduction of input images is designed to mitigate this challenge. Also, our model is trained on these characters---the images we collected for the training dataset are all cropped so that only the characters remain, so that during the training processes the model can learn correlations between certain features and strokes, and the regular patterns of the characters, narrowing the possibilities offered by the blurry images. We also introduce adaptive boosting\cite{adaboost} in our training process, increasing the loss weight of the wrongly reconstructed characters, determined by loss in earlier stages and OCR in later stages, to accommodate the imbalanceness of data. The loss functions in training is also redesigned. The mean square error(MSE) is not suitable in this application, as a misplaced stroke, although highly obstructing readability, may only invoke a slight decrease in MSE because it only influenced a few pixels. Our solution is putting a weight on each pixel before applying weighted MSE. Assuming the characters are black on white, this weight increases at darker pixels and propagates to neighbouring dark pixels so that long strokes and intersections of strokes are given higher weights. This process serves as a supplement to MSE to focus more on readability and is beneficial for OCR and human reading tests. 
\end{itemize}
